Kids stove grades and usage summary

### 2020-02-27 stove_grade_usage_summary.Rmd
summary stat updates
new RMDs for data cleaning

---
title: "Kids stove grades and usage summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 27 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

# Summary of stove grades
```{r}
## Look further into NA values? ##
stove_grade_summary <- stove_grades_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home, stove_grade) %>% 
  #filter(!is.na(stove_grade)) %>% 
  group_by(area, stove_grade) %>% 
  distinct(home) %>% 
  summarize(n())
kable(stove_grade_summary, align = "c")
```

>>>>

---
title: "Kids stove grades and usage summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 27 Feb 2020"
output: pdf_document 
---

@@

```{r}
# Load data
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") 
demographics_clean <- read_rds("Output/demographics_clean.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

############ Use only most recent stove grades for analysis ###############

@@

# Summary of stove grades
```{r}
## Look further into NA values? ##
stove_grade_summary <- stove_grades_clean %>% 
  #filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home, stove_grade, winter_id) %>% 
  #filter(!is.na(stove_grade)) %>% 
  group_by(area, winter_id, stove_grade) %>% 
  distinct(home) %>% 
  summarize(n()) %>% 
  filter(!is.na(stove_grade))
kable(stove_grade_summary, align = "c")

stove_grades_total <- stove_grades_clean %>% 
  filter(!is.na(stove_grade)) %>% 
  filter(!is.na(home)) %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  select(area, home, stove_grade) %>% 
  arrange(area, home) 
```

# Generate random sample of stoves to re-grade and validate grading methods
```{r}
# 10% of homes from each area, earlier winters
# send new ID linked to new ID to Kathrene

random_sample_wmt <- stove_grades_clean %>% 
  select(area, home, stove_grade, winter_id) %>% 
  mutate(winter_id = as.factor(winter_id)) %>% 
  left_join(demographics_clean, c("area", "home", "winter_id")) %>% 
  mutate(cutoff_date = if_else(intervention_date < "2018-06-06", 1, 0)) %>% 
  filter(!is.na(stove_grade)) %>% 
  filter(!is.na(home)) %>% 
  filter(cutoff_date == 1) %>% 
  filter(area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, stove_grade, intervention_date) %>% 
  arrange(area, home) %>% 
  group_by(area) %>% 
  sample_n(17)
write_csv(random_sample_wmt, "Output/random_sample_wmt.csv")

random_sample_nn <- stove_grades_clean %>% 
  select(area, home, stove_grade, winter_id) %>% 
  mutate(winter_id = as.factor(winter_id)) %>% 
  left_join(demographics_clean, c("area", "home", "winter_id")) %>% 
  mutate(cutoff_date = if_else(intervention_date < "2018-06-06", 1, 0)) %>% 
  filter(!is.na(stove_grade)) %>% 
  filter(!is.na(home)) %>% 
  filter(cutoff_date == 1) %>% 
  filter(area == "NN") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, stove_grade, intervention_date) %>% 
  arrange(area, home) %>% 
  group_by(area) %>% 
  sample_n(8)
write_csv(random_sample_nn, "Output/random_sample_nn.csv")

random_sample_ak <- stove_grades_clean %>% 
  select(area, home, stove_grade, winter_id) %>% 
  mutate(winter_id = as.factor(winter_id)) %>% 
  left_join(demographics_clean, c("area", "home", "winter_id")) %>% 
  mutate(cutoff_date = if_else(intervention_date < "2018-06-06", 1, 0)) %>% 
  filter(!is.na(stove_grade)) %>% 
  filter(!is.na(home)) %>% 
  filter(cutoff_date == 1) %>% 
  filter(area == "AK") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, stove_grade, intervention_date) %>% 
  arrange(area, home) %>% 
  group_by(area) %>% 
  sample_n(5)
write_csv(random_sample_ak, "Output/random_sample_ak.csv")
```
